\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2015-11-18 paper/subdocuments/results.Rnw
cleaned results.Rnw
figures

<<different_ginis, fig.cap='Gini coefficients for different income measures',fig.pos='H'>>=
df$G_taxed[df$G_taxed==1]<-NA
library(reshape)
df <- df %>% filter(kanton=="CH"&(bemessungsjahre<=1993.5|bemessungsjahre>=2003))
number_ticks <- function(n) {function(limits) pretty(limits, n)}
dflong <- melt(df[,c("G_steink","G_reink","G_taxed","kanton","bemessungsjahre")], id=c("kanton","bemessungsjahre"))
names(dflong)[3]<-"Income"
names(dflong)[4]<-"Gini"
levels(dflong$Income)<-c("taxable income","net income","taxable income after federal tax")
dflong$Income <- factor(dflong$Income,levels=c("taxable income","taxable income after federal tax","net income"))
fig_incomes <- ggplot(dflong[dflong$kanton=="CH",], aes(x=bemessungsjahre,y=Gini,shape=Income))+
  scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(limits=c(1945,2011),breaks=number_ticks(10)) +
  geom_point(aes(shape=Income),size=pointsize)+
  geom_line(data=dflong[dflong$kanton=="CH",],aes(linetype=Income),size=linesize)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Income definitions within tax data")
fig_incomes
# was ist die maximale Bandbreite zwischen den Punkten?
max(filter(df,kanton=="CH") %>% mutate(d_steink_reink=abs(G_steink-G_reink),d_steink_taxed=abs(G_steink-G_taxed),d_reink_taxed=abs(G_reink-G_taxed)) %>% select(starts_with("d_")),na.rm=TRUE)
# 0.026

@@

<<with_without_zeros_Gini,warning=FALSE, fig.cap='Gini coefficients with, without and imputed non-taxed units',fig.pos='H'>>=
df <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
#library(reshape)
dflong <- melt(df[,c("G_steink","G_steink0","G_steink_halb","kanton","bemessungsjahre")], id=c("kanton","bemessungsjahre"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("without non-taxed","including non-taxed","imputed values for non-taxed")
dflong$Type <- factor(dflong$Type, levels=c("including non-taxed","imputed values for non-taxed","without non-taxed"))
#dflong$Gini[dflong$kanton=="CH"&dflong$bemessungsjahre!=1993.5&dflong$bemessungsjahre<2003&dflong$Type=="including non-taxed"]<-NA
#dflong$Gini[dflong$kanton=="CH"&dflong$bemessungsjahre!=1993.5&dflong$bemessungsjahre<2003&dflong$Type=="imputed values for non-taxed"]<-NA
fig_zeros <- ggplot(filter(dflong,kanton=="CH"&
  (((bemessungsjahre<=1993.5|bemessungsjahre>=2003)&Type=="without non-taxed")|
  ((bemessungsjahre==1993.5|bemessungsjahre>=2003)&Type!="without non-taxed"))), 
       aes(x=bemessungsjahre,y=Gini,shape=Type,linetype=Type))+
  scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(limits=c(1970,2011),breaks=number_ticks(10)) +
  geom_line(size=linesize)+
  geom_point(aes(shape=Type),size=pointsize)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Influence of non-taxed")
fig_zeros

@@

bern <- filter(bern,Satzeink_KANTON<=TOTEINK,erm==0)
bern <- filter(bern,Satzeink_BUND<=TOTEINK,erm==0)
bern$verfeink<-bern$TOTEINK+bern$privattrans_bez-bern$steuertotal

@@

# wide to long
bern_gini_long <- melt(bern_gini,id.vars="stj",variable.name="Income",value.name="Gini")
names(bern_gini_long)<-c("stj","Income","Gini")
# legend order
levels(bern_gini_long$Income) <- c("total income", "taxable income", "disposable income")
bern_gini_long$Income <- factor(bern_gini_long$Income,levels=c("total income", "taxable income", "disposable income"))
bern_gini_long$Income <- factor(bern_gini_long$Income,levels=c("taxable income","total income","disposable income"))

>>>>

<<different_ginis, fig.cap='Gini coefficients for different income measures',fig.pos='H'>>=
df$G_taxed[df$G_taxed==1]<-NA
library(reshape)
df <- df %>% filter(kanton=="CH"&(bemessungsjahre<=1993.5|bemessungsjahre>=2003))
number_ticks <- function(n) {function(limits) pretty(limits, n)}
dflong <- melt(df[,c("G_steink","G_reink","G_taxed","kanton","bemessungsjahre")], id=c("kanton","bemessungsjahre"))
names(dflong)[3]<-"Income"
names(dflong)[4]<-"Gini"
levels(dflong$Income)<-c("taxable income (total income - all deductions)","net income (total income - non-social deductions)","taxable income after federal tax")
dflong$Income <- factor(dflong$Income,levels=c("taxable income (total income - all deductions)","taxable income after federal tax","net income (total income - non-social deductions)"))
fig_incomes <- ggplot(dflong[dflong$kanton=="CH",], aes(x=bemessungsjahre,y=Gini,shape=Income))+
  scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(limits=c(1945,2011),breaks=number_ticks(10)) +
  geom_point(aes(shape=Income),size=pointsize)+
  geom_line(data=dflong[dflong$kanton=="CH",],aes(linetype=Income),size=linesize)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Income definitions within tax data")
fig_incomes
# was ist die maximale Bandbreite zwischen den Punkten?
max(filter(df,kanton=="CH") %>% mutate(d_steink_reink=abs(G_steink-G_reink),d_steink_taxed=abs(G_steink-G_taxed),d_reink_taxed=abs(G_reink-G_taxed)) %>% select(starts_with("d_")),na.rm=TRUE)
# 0.026

@@

<<with_without_zeros_Gini,warning=FALSE, fig.cap='Gini coefficients with, without and imputed non-taxed units',fig.pos='H'>>=
df <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
#library(reshape)
dflong <- melt(df[,c("G_steink","G_steink0","G_steink_halb","kanton","bemessungsjahre")], id=c("kanton","bemessungsjahre"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("without non-taxed","including non-taxed","imputed values for non-taxed")
dflong$Type <- factor(dflong$Type, levels=c("including non-taxed","imputed values for non-taxed","without non-taxed"))
#dflong$Gini[dflong$kanton=="CH"&dflong$bemessungsjahre!=1993.5&dflong$bemessungsjahre<2003&dflong$Type=="including non-taxed"]<-NA
#dflong$Gini[dflong$kanton=="CH"&dflong$bemessungsjahre!=1993.5&dflong$bemessungsjahre<2003&dflong$Type=="imputed values for non-taxed"]<-NA
fig_zeros <- ggplot(filter(dflong,kanton=="CH"&
  (((bemessungsjahre<=1993.5|bemessungsjahre>=2003)&Type=="without non-taxed")|
  ((bemessungsjahre==1993.5|bemessungsjahre>=2003)&Type!="without non-taxed"))), 
       aes(x=bemessungsjahre,y=Gini,linetype=Type))+
  scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(limits=c(1970,2011),breaks=number_ticks(10)) +
  #scale_linetype_manual("Taxable income",values=c("including non-taxed"=1,"imputed values for non-taxed"=2,"without non-taxed"=3))+
  #scale_shape_manual("Taxable income",values=c("including non-taxed"=1,"imputed values for non-taxed"=2,"without non-taxed"=3))+
  geom_line(size=linesize)+
  geom_point(aes(shape=Type), fill = "red",size=pointsize)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Influence of non-taxed")+
  labs(shape="Taxable income")+
  labs(linetype="Taxable income")
fig_zeros

@@

bern <- filter(bern,Satzeink_KANTON<=TOTEINK,erm==0)
bern$verfeink<-bern$TOTEINK+bern$privattrans_bez-bern$steuertotal

@@

# wide to long
bern_gini_long <- melt(bern_gini,id.vars="stj",variable.name="Income",value.name="Gini")
names(bern_gini_long)<-c("stj","Income","Gini")
# legend order
levels(bern_gini_long$Income) <- c("total income (earnings, self-employment, capital income)", "taxable income (total income - all deductions)", "disposable income (total income - taxes: federal, cantonal, communal and churches)")
bern_gini_long$Income <- factor(bern_gini_long$Income,levels=c("total income (earnings, self-employment, capital income)", "taxable income (total income - all deductions)", "disposable income (total income - taxes: federal, cantonal, communal and churches)"))
bern_gini_long$Income <- factor(bern_gini_long$Income,levels=c("taxable income (total income - all deductions)","total income (earnings, self-employment, capital income)","disposable income (total income - taxes: federal, cantonal, communal and churches)"))
